# html-colors

```{r}
#| eval: false
#| include: false

library(dplyr, quietly = TRUE)
library(here, quietly = TRUE)
library(knitr, quietly = TRUE)
library(magrittr, quietly = TRUE)
library(purrr, quietly = TRUE)
library(readr, quietly = TRUE)
library(simplermarkdown, quietly = TRUE)
library(yaml, quietly = TRUE)
```

```{r}
#| include: false

library(magrittr)
```

<!-- badges: start -->
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![Espanso Hub](https://img.shields.io/badge/Espanso%20Hub-0.1.0-%2300A595.svg)](https://hub.espanso.org/html-colors)
[![License: MIT](https://img.shields.io/badge/license-MIT-green)](https://choosealicense.com/licenses/mit/)
[![Contributor Covenant](https://img.shields.io/badge/Contributor%20Covenant-2.1-4baaaa.svg)](https://www.contributor-covenant.org/version/2/1/code_of_conduct/)
<!-- badges: end -->

## Overview

`html-colors` is an [Espanso](https://espanso.org) package that allows you to insert HTML color codes into your text seamlessly. By using this package, shortcuts like `##red` are automatically replaced with their corresponding hex color codes (e.g., `#FF0000`). You can also retrieve RGB color codes and the color family. It is designed to work in conjunction with the [`html-utils-package`](https://hub.espanso.org/html-utils-package).

This package is inspired by [Jenny Knuth's gist](https://gist.github.com/jennyknuth/e2d9ee930303d5a5fe8862c6e31819c5). A big thank you to Jenny!

## Installation

To install the latest released version of `html-colors`, use [Espanso Hub](https://hub.espanso.org/):

``` sh
espanso install html-colors
```

To install the development version directly from GitHub, use:

``` sh
espanso install html-colors --git https://github.com/danielvartan/html-colors/ --external
```

## Usage

Once installed, `html-colors` will replace the specified shortcuts with their corresponding character as you type.

```{r}
#| echo: false

match_file <- here::here("src", "package.yml")
```

```{r}
#| echo: false

data <- 
  match_file |>
  readr::read_lines(skip = 1) %>%
  yaml::read_yaml(text = .) |>
  purrr::map_dfr(tibble::as_tibble) |>
  dplyr::mutate(
    hex_code = dplyr::case_when(
      stringr::str_detect(trigger, "rgb-") ~ dplyr::lag(replace, n = 1),
      stringr::str_detect(trigger, "families-") ~ dplyr::lag(replace, n = 2),
      TRUE ~ replace
    )
  ) |>
  dplyr::mutate(
    hex_code = stringr::str_replace(hex_code, "#", ""),
    color = paste0(
        "![#",
        hex_code,
        "](images/",
        hex_code,
        ".png)"
    ),
    trigger = paste0("`", trigger, "`"),
    replace = paste0("`", replace, "`")
  )
```

```{r}
#| echo: false

data <- 
  data |>
  dplyr::select(trigger, replace, color) |>
  dplyr::rename(
    Trigger = trigger,
    Result = replace,
    Color = color
  )
```

```{r}
#| echo: false
#| output: "asis"

simplermarkdown::md_table(data)
```

## Prefix

The `##` prefix was used to avoid conflicts with social media hashtags and the [`html-utils-package`](https://hub.espanso.org/html-utils-package).

## Contributing

If you feel like there's any important tag/snippet missing, feel free to create a Pull Request or open an [Issue](https://github.com/danielvartan/html-colors/issues/new).

## License

[![License:
MIT](https://img.shields.io/badge/license-MIT-green)](https://opensource.org/license/mit/)

`html-colors` code is released under the [MIT license](https://opensource.org/license/mit/).
